---
title: "Appendix"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Figure 1: Description of Data
```{r}
movie = read.csv("movie.csv")
colnames(movie)
```
- `X`: The unique identifiers of each observation  
- `ReleaseDate`: When the movie released  
- `Title`: The title of the movie  
- `ProductionBudget`: The amount of money spent to produce the movie.   
- `OpeningWeekend`: How much the movie earned during the weekend it released  
- `DomesticBox.Office`: How much the movie earned in the United States  
- `WorldwideBox.Office`: How much the movie earned globally  
- `Trailer`: Whether a movie released a trailer or not. **1** = True, **0** = False  
- `MPAA_Rating`: The MPAA Rating of the movie  
- `Production_Method`: How the movie was made. eg live action, animation, etc.  
- `Genre`: Genre of the movie  
- `Running_Time`: The duration of the movie  
- `Keywords`: Words that releate to the movie. eg, avatar is about aliens so alien is a keyword for avatar  
- `Franchise`: Whether a movie has a franchise. **1** = true, **0** = false  
- `Production_Companies`: The company that made the movie  
- `Production_Countries`: The country the movie is produced in   
- `Source`: The source of the movie. eg book, folktales, etc  
- `Creative_Type`: The creative type of movie. eg: fiction, nonfiction, factual,etc.  
- `Year`: The year the movie released  
- `month`: the month the movie released  
- All other variables (`warner`, `Columbia`, `Universal_Pictures`, `Walt_Disney_Pictures`,`Marvel_Studios`, `Paramount_Pictures`,`Century_Fox`, `Relativity_Media`, `DreamWorks_Pictures`, `New_Line_Cinema`, `Regency_Enterprises`, `Lionsgate`,`BBC_Films`, `StudioCanal`, `Working_Title_Films`, `Blumhouse`, `BFI`, `France`, `Cine_Plus`, `Participant_Media`, `Village_Roadshow_Productions`, `Metro_Goldwyn_Mayer_Pictures`) are production companies, **1** = the company made the movie, **0** = the company did not make that movie.  


