---
title: "Data_visu"
author: "Seung ji Nam"
date: '2018 12 17 '
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#read movie data
movie=read.csv("Movie_Analysis/movie.csv",stringsAsFactors = FALSE,check.names=FALSE)
movie
#change the row name
row.names(movie)=movie$X
#delete the first column
movie=movie[,-1]
#delete the unuseful and unappropriate variables
movie=movie[,c(-1,-2,-4,-5,-12,-14,-15)]
#delete the observations that has NA values
movie=na.omit(movie)
movie_dummy <- read.csv("Movie_Analysis/movie_dummy.csv")
```

```{r eval=F, echo=F}
# Dummy Variable of Production Countries
movie_dummy <- read.csv("Movie_Analysis/movie_dummy.csv")

Production_Countries.US <- as.numeric(movie_dummy$Production_Countries=="United States")
Production_Countries.NonUS <- as.numeric(movie_dummy$Production_Countries!="United States")
Production_Countries_dummy <- cbind(Production_Countries.US,Production_Countries.NonUS)

movie_dummy<- cbind(movie_dummy, Production_Countries_dummy)
write.csv(movie_dummy, file="movie_dummy.csv")
```
```{r echo=F, eval=F}
movie_dummy <- movie_dummy[,-c(110:113)]
write.csv(movie_dummy, file="movie_dummy.csv")
```


```{r}
# Linear Regression about Budget
fit1 <- lm(`WorldwideBox.Office`~ ProductionBudget + OpeningWeekend + DomesticBox.Office , data=movie_dummy)
summary(fit1)
coef
```
Among varaibles related to budgets, `DomesticBox.Office`is the best variable to explain `WorldwideBox.Office`. Also, `DomesticBox.Office`, `OpeningWeekend`,`ProductionBudget` are all have signifcantly high correlation. Therefore, I used only `DomesticBox.Office`, not `OpeningWeekend` and `ProductionBudget`. 

```{r}
library(ggplot2)
# geom_point between DomesticBox.Office and WorldwideBox.office
ggplot(data=movie_dummy,aes(x=DomesticBox.Office, y=WorldwideBox.Office)) +
  geom_point(size=0.2)

# limit the range of x
ggplot(data=movie_dummy,aes(x=DomesticBox.Office, y=WorldwideBox.Office)) +
  geom_point(size=0.2) +
  xlim(0,5.0e+08) 

# facet_wrap by Production countries 
ggplot(data=movie_dummy,aes(x=DomesticBox.Office, y=WorldwideBox.Office)) +
  geom_point(size=0.2,na.rm=F) +
  facet_wrap(~ Production_Countries.US)

# face_wrap + limit the range of x
ggplot(data=movie_dummy,aes(x=DomesticBox.Office, y=WorldwideBox.Office)) +
  geom_point(size=0.2,na.rm=F) +
  facet_wrap(~ Production_Countries.US)+
  xlim(0,5.0e+08) 
```

```{r}
# correlation among variables related to money
library(corrplot)
pr.cor<- cor(na.omit(movie_d[,4:7]));pr.cor
corrplot(pr.cor,method="number",type='lower')

```



```{r}
# geom_bar between month and Worldwide Box office in time order 
library(ggplot2)
month_data <-data.frame(month=factor(movie$month,levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")),'WorldwideBox Office'=movie$'WorldwideBox Office')

ggplot(data=month_data, aes(x=month, y=WorldwideBox.Office)) +
 geom_boxplot()
```
```{r}

ggplot(data=movie_dummy, aes(x=Year, y=WorldwideBox.Office)) +
  geom_point(size=0.4,na.rm=T) 
  
ggplot(data=movie_dummy, aes(x=Year, y=WorldwideBox.Office)) +
  geom_jitter(size=0.3,na.rm=T) +
  xlim(1990,2021)

```
`month` semms to have some kind of trend related to `WorldwideBox.office`. There seems to be a trend that `WorldwideBox.office` gets higher from the beginning of the year to the end of the year. 

```{r}
# WorldwideBox.office and OpeningWeekend by trailer
ggplot(data=movie_dummy, aes(x=OpeningWeekend, y=WorldwideBox.Office)) +
   geom_point(size=0.3,na.rm=T) +
  facet_wrap(~ Trailer)+
  xlim(0,1e+08)

```
Whether there is a `Trailer` or not, it seems `OpeningWeekend` and `WorldwideBox.Office` is related. 


```{r}
table(movie$Genre)
ggplot(data=movie, aes(Genre)) +
  geom_bar()
# Let's put Black Comedy, Concert/Performance, Documentary, Musical, Western to etc. 
genre_data <- movie$Genre
genre_data[genre_data %in% c('Black Comedy','Concert/Performance','Documentary','Musical','Western')]<- "Etc"

ggplot(data=as.data.frame(genre_data),aes(genre_data)) +
  geom_bar()
```
Among `Genre`, Drama, Action, Adventure, Comedy are the most prevalent. 

```{r}
Year_data<- movie$Year
Year_data[Year_data %in% c(1930:2000)] <- "1930~2000"
Year_data[Year_data %in% c(2001:2010)]<- "2001~2010"
Year_data[Year_data %in% c(2011:2020)]<- "2011~2020"

genrefit <- as.data.frame(cbind(movie$`WorldwideBox Office`, genre_data, "Year"=Year_data))
genre.fit <- lm(movie$`WorldwideBox Office`~ genre_data, data=genrefit)
summary(genre.fit)
```
All genres are quite significant. 
```{r}
ggplot(data=genrefit, aes(x=genre_data, y=movie$`WorldwideBox Office`)) +
 geom_bar(stat="identity")

ggplot(data=genrefit, aes(x=genre_data,y=movie$`WorldwideBox Office`)) +
  geom_bar(stat="identity") +
  facet_wrap(~Year) +
  theme(axis.text.x=element_text(angle=60,hjust=1))

```

Adventure and Action `Genre` are significant related to `WorldwideBox Office`. 

```{r}
# Production company
product_com <- as.data.frame(table(movie_dummy$Production_Companies))
product_com$Var1[product_com$Freq >=20]
Companies<- as.data.frame(cbind(movie_dummy$WorldwideBox.Office, movie_dummy$Production_Companies))

```
```{r}
# About the storyline of movie (Creative_Type, genre, Source)
ggplot(data=movie,aes(x=Creative_Type, y=`WorldwideBox Office`)) +
  geom_bar(stat="identity")
```
```{r}
movie_source <- movie[movie$Source==c("Based on Comic/Graphic Novel","Based on Factual Book/Article","Based on Fiction Book/Short Story","Based on Folk Tale/Legend/Fairytale","Based on Real Life Events","Based on TV","Original Screenplay","Remake"),]


ggplot(data=movie_source,aes(Source))+
  geom_bar() +
  theme(axis.text.x=element_text(angle=60,hjust=1))

ggplot(data=movie_source, aes(x=Source, y=`WorldwideBox Office`)) +
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle=60,hjust=1))

ggplot(data=movie_source,aes(x=Genre,y=`WorldwideBox Office`)) +
  geom_bar(aes(fill=Source),stat="identity") +
  theme(axis.text.x = element_text(angle=60,hjust=1))
  

ggplot(data=movie_source, aes(x=Genre, y=`WorldwideBox Office`)) +
 geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle=60,hjust=1)) +
  facet_wrap(~ Source)
```
Based on Book/ Short Story, and 'Original Screenplay' movies had high `WorldwideBox Office`. 

```{r}
genrefit <- as.data.frame(cbind(movie$`WorldwideBox Office`,genre_data))
genre.fit <- lm(movie$`WorldwideBox Office`~ genre_data, data=genrefit)
summary(genre.fit)
```
```{r}
ggplot(data=genrefit, aes(x=genre_data, y=movie$`WorldwideBox Office`)) +
 geom_bar(stat="identity")

```
```{r}
# Production Companies that have at least 10 movies

log <- movie_dummy$Production_Companies %in% c("Warner Bros.","Regency Enterprises","Working Title Films","Columbia Pictures","Castle Rock Entertainment","Walt Disney Pictures","Participant Media","Universal Pictures","20th Century Fox","Gold Circle Films","Blumhouse","DreamWorks Animation","Marvel Studios","Touchstone","Pictures","Twentieth Century Fox","Amblin Entertainment","DreamWorks Pictures","Jersey Films","Metro-Goldwyn-Mayer Pictures","Davis Entertainment","Tri-Star Pictures","Lucasfilm","Revolution Studios","Silver Pictures","Eon Productions, United Artists","Lakeshore Entertainment","Village Roadshow Productions","Walt Disney Animation Studios")
movie_comp <- cbind(movie_dummy[log,], "Production_Method"=movie[log,"Production_Method"] )


ggplot(data=movie_comp,aes(x=Production_Companies, y=WorldwideBox.Office)) +
         geom_bar(stat="identity", aes(fill=Production_Method)) +
          theme(axis.text.x = element_text(angle=60,hjust=1)) 

ggplot(data=movie, aes(Production_Method)) +
  geom_bar()
         
```
Because most of `Production_Method` is Live Action, `Production_Method` doesn't matter much to `WorldwideBox.Office`. 

```{r}
a
movie_dummy$Production_Companies %in% c("Warner Bros.","Regency Enterprises","Working Title Films","Columbia Pictures","Castle Rock Entertainment","Walt Disney Pictures","Participant Media","Universal Pictures","20th Century Fox","Gold Circle Films","Blumhouse","DreamWorks Animation","Marvel Studios","Touchstone","Pictures","Twentieth Century Fox","Amblin Entertainment","DreamWorks Pictures","Jersey Films","Metro-Goldwyn-Mayer Pictures","Davis Entertainment","Tri-Star Pictures","Lucasfilm","Revolution Studios","Silver Pictures","Eon Productions, United Artists","Lakeshore Entertainment","Village Roadshow Productions","Walt Disney Animation Studios")
```

```{r}
 movie
        
  
```

